---
title: "final_project"
author: "Cristopher Patvakanian"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Putting in all of the necessary libraries

library(httr)
library(knitr)
library(dplyr)
library(glue)
library(readxl)
library(janitor)
library(reprex)
library(readxl)
library(lubridate)
library(xml2)
library(anytime)
library(moderndive)
library(gt)
library(maps)
library(png)
library(purrr)
library(reprex)
library(stargazer)
library(tibble)
library(forcats)
library(infer)
library(fs)
library(devtools)
library(rworldmap)
library(googlesheets4)
library(infer)
library(ggplot2)
library(scales)
library(tidyverse)

```

## Setting up and Reading in Data
We can see the cleaned data being read in here.

```{r Setting up Data, message = FALSE,  warning=FALSE}

# I included message equals false because even
# after parsing the columns as false and asking
# in study halls, we were unable to clear the
# message asking me to read in the data with
# particular columns

# Data is from embassies website: https://www.embassypages.com/armenia

embassies <- read_csv(file = 'embassies.csv')

# Merged data of communities, embassies, top google trends

all_data_merged <- read_csv(file = "all_data.csv") %>%
  slice(1:26)


```



```{r MapGraphic 1, echo = FALSE, include = FALSE, warning = FALSE, message = FALSE}

# Using joinCountryData to create maps
# about Armenian Diaspora
# this is the maps for the homepage

# I have used warning, include, and message
# equals false for all of these r chunks
# that use the MapCountryData because I was
# unable to get rid of the messages which automatically
# come included with the package about which countries
# I include and which ones I didn't

d <- data.frame(
  country=c("Argentina", "Brazil", "Bulgaria", "Canada", "Egypt",
             "France", "Georgia", "Germany", "Greece","Iran",
            "Iraq", "Kazakhstan", "Lebanon", "Russia", "Sweden","Syria", "Turkmenistan", "Ukraine", "United Kingdom",
           "United States", "Turkey", "Uzbekistan", "Uruguay", "Australia", "Switzerland", "Israel"),
  value=c(2, 2, 2, 2, 2,2, 2, 2, 1, 2, -2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2))

n <- joinCountryData2Map(d, joinCode="NAME", nameJoinColumn="country")

png("diaspora_final_project/world_map.png",width=800,height=600,units="px")
world <- mapCountryData(n, nameColumnToPlot="value", mapTitle="Overview of Armenian Diaspora Communities in the World",
  mapRegion = "World",
  colourPalette="Red",
  addLegend=FALSE,
  oceanCol="lightblue", missingCountryCol="white")

```


```{r MapGraphic2, message = FALSE, warning=FALSE}

#Second Map for the homepage

png("diaspora_final_project/eurasia_map.png",width=800,height=600,units="px")
eurasia <- mapCountryData(n, nameColumnToPlot="value", mapTitle="Overview of Armenian Diaspora Communities in Eurasia",
  mapRegion = "Eurasia",
  colourPalette="Red",
  addLegend=FALSE,
  oceanCol="lightblue", missingCountryCol="white")

```


```{r MapGraphic3, echo = FALSE, include = TRUE, warning = FALSE, message = FALSE}

# Third Map for the homepage

png("diaspora_final_project/latin_map.png",width=800,height=600,units="px")
latin <- mapCountryData(n, mapTitle="Overview of Armenian Diaspora Communities in South America", nameColumnToPlot="value", 
  mapRegion = "Latin America",
  colourPalette="Red",
  addLegend=FALSE,
  oceanCol="lightblue", missingCountryCol="white")

```



```{r histogram, include = TRUE, warning=FALSE}

# here I am manipulating the data
# to be read as integers in order
# to be able to feed it into my histogram
# on the home page

# I am using warning=False here because
# it says NAs introduced by coercion,
# but it is unclear, despite my best efforts
# why they are being introduced

all_data_merged %>% mutate_if(is.character,as.integer)

all_data_merged$Number_Comm <- as.integer(all_data_merged$Number_Comm)

data_histogram <- all_data_merged %>%
  select(Population,Number_Comm)

histo.df <- as.data.frame(data_histogram)

write_rds(histo.df, "diaspora_final_project/histo.rds")

```


```{r Diaspora Data Highlights,echo = FALSE, include = FALSE, warning = FALSE, message = FALSE}

# here I am specifing countries which
# have diasporas from the times of 
# Armenian genocide immigrants fleeing
# from Western Armenia in 1915

d3 <- data.frame(
  country=c("Argentina", "Canada",
             "France", "Georgia", "Greece",
             "Lebanon", "Russia", "Syria", "Ukraine", 
           "United States", "Turkey",  "Uruguay", "Australia", "Israel"),
  value=c(2, 2, 2, 2, 2, 2, 2, 2, -2, 2, 2, 2, 2, 2))

n3 <- joinCountryData2Map(d3, joinCode="NAME", nameJoinColumn="country")

png("diaspora_final_project/diasporasgenocide.png",width=800,height=600,units="px")
mapCountryData(n3, nameColumnToPlot="value", mapTitle="Diasporas from Armenian Genocide",
  mapRegion = "World",
  colourPalette="negpos8",
  addLegend=FALSE,
  oceanCol="lightblue", missingCountryCol="white",
  lwd = 0.7)


# This map here is showing us
# the diasporas which exist after
# the USSR collapsed and typically
# attributing to existing bc of the
# soviet union

d4 <- data.frame(
  country=c("Bulgaria", "Canada","Brazil",
             "France", "Georgia", "Germany", "Greece",
            "Kazakhstan", "Russia", "Turkmenistan", "Ukraine",
           "United States", "Uzbekistan"),
  value=c(2, 2, 2, 2, 2, 2, 2, 2, -2, 2, 2, 2,2))

n4 <- joinCountryData2Map(d4, joinCode="NAME", nameJoinColumn="country")

png("diaspora_final_project/postsoviet.png",width=800,height=600,units="px")
mapCountryData(n4, nameColumnToPlot="value", mapTitle="Post Soviet Diasporas",
  mapRegion = "World",
  colourPalette="white2black",
  addLegend=FALSE,
  oceanCol="lightblue", missingCountryCol="white",
  lwd = 0.7)

# These are Diasporas which exist
# for very specific historic reasons
# and also reasons which realy have
# no particular special explanation other
# other than migration for economic

d5 <- data.frame(
  country=c( "Egypt",
            "Iran",
            "Iraq", "Sweden","Syria","United Kingdom", "Germany",
            "Switzerland", "Israel"),
  value=c(2, 2, 2, 1, 2, 2, -2, 2,2))

n5 <- joinCountryData2Map(d5, joinCode="NAME", nameJoinColumn="country")

png("diaspora_final_project/historic.png",width=800,height=600,units="px")
mapCountryData(n5, nameColumnToPlot="value", mapTitle="Historic or Random Diasporas",
  mapRegion = "Eurasia",
  colourPalette="palette",
  addLegend=FALSE,
  oceanCol="lightblue", missingCountryCol="white",
  lwd = 0.7)



```

## Creating Correlation Graphic
We can see the correlation graphic being created here and some of those summary statistics.

```{r What Influences Number of Communities, include = TRUE}

# Here I am using this data to show
# a correlation or simple regression of 
# number of communities with population

regression_for_graph <- lm(Number_Comm ~ Population, data = all_data_merged)
summary(regression_for_graph)


png("diaspora_final_project/regression.png",width=800,height=600,units="px")
regression_graph <- ggplot(regression_for_graph, aes(x= Population, y = Number_Comm)) +
  geom_point( alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Number of Communities vs Population", subtitle = "Relationship Looks Positive", caption= "Wikipedia",
       x = "Population Numbers (Official & Estimates)", y = "Number of Communities in a Country")

```
## Multivariate Regression Summary Statistics
Here we have the summary statistics of the multivariate regression.

```{r multivariate regression}

# Regression of data, but this is very
# tricky to try and visualize because
# the x variables are both continous
# and binary and the y is continuous
# so I'd have to hold some things constant
# I am not quite sure what's the best way to
# visualize this

no_russia <- all_data_merged %>%
  filter(Country !="Russia")

no_russia <- lm(Population ~ TopTen_Gen + TopTen_Dux + Number_Comm + Embassies + Number_Comm + Post_Soviet, data = no_russia)
summary(no_russia)

```

## Multivariate Regression Output Using StarGazer
Here we have the regression table output.

```{r getting table to be output, warning=FALSE, results='asis'}

# Here I have just created the output
# for the multivariate regression in a 
# nice table format

# I needed to include warning=FALSE and
# results='asis' in order to get rid of the
# output which appears in my markdown that 
# is part of the functionality of stargazer
# and to the best of my understanding not
# an issue with the regression

stargazer(no_russia, type = "html", title=" ", digits=1, 
          covariate.labels=c("Top 10 Genocide Search","Top 10 Duxov Search","Number of Communities",
 "Has an Armenian Embassy","Post Soviet Country"), 
          out="regression.html")

```


## Making Sidebar Panel
Here we can see the data I used to create the sidebar panel.


```{r making sidebarpanel, message= FALSE}

# Loading in previously cleaned data from Wikipedia
# to have my sidebar panel created

diasporas <- read_csv(file = 'diaspora_data.csv') 

diasporas %>%
  slice(1:68) %>%
  mutate(Population = Population/1000)

diasporas.df <- as.data.frame(diasporas)

write_rds(diasporas.df, "diaspora_final_project/diasporasA.rds")

```

## About Page Data:


```{r About}

# Had the about completed from a previously
# completed milestone project
```
## About the Armenian Diaspora Data Project
This project is trying to better understand the trends and characteristics of the Armenian Diaspora communities which exist all over the world. Armenian Diaspora communities have existed for hundreds of years, but the primary large communities that scattered and exist today come from two major events in Armenian history. The first event was the Armenian Genocide of 1915, during which 1.5 Armenians and many other Christian minorities such as the Assyrians and Greeks were killed due to the genocidal campaign of the Ottoman Turkish government. The result of the genocide was the mass exodus of Armenians to countries such as Syria, France, Lebanon, Russia, the United States, Australia and even Argentina. The second major event which explains the diaspora communities of that exist in other parts of the world was the collapse of the USSR and subsequent socio-economic crisis, after which many Armenians immigrated to the United States, Russia, and various other countries. Of course, there also exist other older, but much smaller communities in Jerusalem and India - which have ties back to ancient Armenian religious ties and trade expeditions.

## Data on the Diaspora
Finding data on the Armenian Diaspora is notoriously difficult, but Wikipedia and Google trends are able to capture a rough idea of where Armenians are generally located. By looking at compilations of various sources on Wikipedia's Armenian Diaspora Communities page (https://en.wikipedia.org/wiki/Largest_Armenian_diaspora_communities), I am able to confirm for a variety of countries the number of communities and also the populations of those communities. Additionally, by looking at data on the Google Trends Website (https://trends.google.com/trends/?geo=US), I am able to look at these countries and try to look at trends or key words for Armenians that I think might confirm the census data. Interestingly, there are different and similar trends for Armenians depending on which community we are looking at (old vs newly formed).

## About the Author
I am a senior at Harvard College studying Economics with a minor in Government.


